Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-10 WSSSPE4_report/WSSSPE4_report.tex
fixing name collision

\item \textbf{Anshu Dubey and Katherine Riley: \emph{Experience Paper: Software
Engineering and Community Codes Track in ATPESC}}~\cite{Dubey:2016ws}.
The Argonne Training Program in Extreme Scale
Computing (ATPESC) was started by Argonne National Laboratory with the objective
of expanding the ranks of better prepared users of high-performance computing (HPC) machines.
One of the unique aspects of the program was inclusion of a
software engineering and community codes track. The inclusion
was motivated by the observation that the projects with a good
software process were better able to meet their scientific goals.
The paper presents the experience in running the software
track, the motivation, reception, and evolution of the track over the years.
The authors recommend the inclusion of similar tracks in other HPC-oriented training programs.

@@

\item \textbf{Anshu Dubey and Lois Curfman McInnes: \emph{Idea Paper: The Lifecycle
of Software for Scientific Simulation}}~\cite{Dubey:2016ws}.
The authors discuss the specifics of the lifecycle of scientific software.
While the software lifecycle is a well-researched topic, one class of projects,
research software, has received relatively
little attention from lifecycle researchers. This
paper formalizes a lifecycle model
for end-to-end scientific application software, featuring loose
coupling between submodels for development of infrastructure
and scientific capability. The authors also invite input from stakeholders
to converge on a model that captures the complexity of this
development processes and provides needed lifecycle guidance to
the scientific software community.

>>>>

\item \textbf{Anshu Dubey and Katherine Riley: \emph{Experience Paper: Software
Engineering and Community Codes Track in ATPESC}}~\cite{Dubey1:2016ws}.
The Argonne Training Program in Extreme Scale
Computing (ATPESC) was started by Argonne National Laboratory with the objective
of expanding the ranks of better prepared users of high-performance computing (HPC) machines.
One of the unique aspects of the program was inclusion of a
software engineering and community codes track. The inclusion
was motivated by the observation that the projects with a good
software process were better able to meet their scientific goals.
The paper presents the experience in running the software
track, the motivation, reception, and evolution of the track over the years.
The authors recommend the inclusion of similar tracks in other HPC-oriented training programs.

@@

\item \textbf{Anshu Dubey and Lois Curfman McInnes: \emph{Idea Paper: The Lifecycle
of Software for Scientific Simulation}}~\cite{Dubey2:2016ws}.
The authors discuss the specifics of the lifecycle of scientific software.
While the software lifecycle is a well-researched topic, one class of projects,
research software, has received relatively
little attention from lifecycle researchers. This
paper formalizes a lifecycle model
for end-to-end scientific application software, featuring loose
coupling between submodels for development of infrastructure
and scientific capability. The authors also invite input from stakeholders
to converge on a model that captures the complexity of this
development processes and provides needed lifecycle guidance to
the scientific software community.
